---
title: "Analysis of echo parameters and others"
author: "Filimonova Irina"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, error = FALSE)
library(readxl)
library(tidyverse)
library(GGally)
library(ggcorrplot)
library(pheatmap)
library(factoextra)
library(scales)
library(rstatix)
library(ggpubr)
library(ggfortify)
library(car)
library(flextable)
library(sandwich)
library(gtsummary)
library(lmtest)
library(gt)
library(modelsummary)

df1_no_date <- read.csv("data/interim/df1_no_date.csv")

df1 <- read_csv("data/interim/df1.csv")
df1 <- df1 %>% 
  mutate(Year_sx_date = year(Sx_Date)) %>% 
  mutate(across(c(Upsizing, OS_Event), \(x) fct_recode(factor(x), 
                                                      "No" = "0",
                                                      "Yes" = "1")))
```

# Correlation analysis

```{r}
df1_no_date <- df1_no_date %>% 
  mutate(Upsizing_num = if_else(Prosthesis_Size>Prosthesis_Anat_Size, Prosthesis_Size - Prosthesis_Anat_Size, if_else(Prosthesis_Size <= Prosthesis_Anat_Size, 0, NA))) 

# Percentage of missing values
#df1_no_date %>% 
# map(\(x) sum(is.na(x))/length(x))

# Delete columns if more than 50% of values are NA
df1_no_na_col <- df1_no_date %>% select(where(\(x) sum(!is.na(x))/length(x) >= 0.5))

Pre_MPG <- df1_no_date$Pre_MAVG_MPG

df1_no_na_col_MPG<- cbind(df1_no_na_col, Pre_MPG)
```


```{r}
cleaned_data_num <- df1_no_na_col_MPG |>
              select("Age", "Height", "Weight" , "BMI", "STS", "Sx_Duration_Min",  "Sx_Cardiopulm_Bypass_t", "Sx_Aort_Clamp_t", "Pre_LVEF", "Upsizing_num" , "Pre_MPG")


# Visualization
plot_cor <- ggcorrplot(cor(cleaned_data_num %>% 
              drop_na()), tl.cex = 11)
plot_cor

ggsave("data/pics/plot_cor.png", plot_cor, dpi = 200, width = 6, height = 4)
```


# Additional graphs for EDA

## Bar plot of pattern over the years of replacement of aortic valve

```{r}
ggplot(df1, aes(x = Year_sx_date, fill =Upsizing)) +
  geom_bar(position = "dodge") +
  labs(x = "Year",
       y = "Count") +
  scale_x_continuous(breaks = seq(2011, 2021, 1)) +
  theme_bw() +
  theme(plot.title = element_text(size = 14, hjust = 0.5),
        axis.title = element_text(face = 'bold'),
        axis.text.x = element_text(angle= 90 , vjust= 0.5 , hjust= 1 ))

```

## + percent of operations

```{r}
ggplot(df1, aes(x = Year_sx_date, fill =Upsizing)) +
  geom_bar(position = "fill") +
  labs( x = "Year",
       y = "Percent") +
  scale_x_continuous(breaks = seq(2011, 2021, 1)) +
  scale_y_continuous(labels = percent) +
  theme_bw() +
  theme(plot.title = element_text(size = 14, hjust = 0.5),
        axis.title = element_text(face = 'bold'),
        axis.text.x = element_text(angle= 90 , vjust= 0.5 , hjust= 1 ))

```

## Box plot of STS from the outcome depending on the type of prosthetics.

```{r}
ggplot(df1) +
  geom_boxplot(aes(x = Upsizing, y = STS, fill = OS_Event)) +
  labs(x = "Upsizing", y = "STS") +
  theme_bw() +
  theme(plot.title = element_text(size = 14, hjust = 0.5),
        axis.title = element_text(face = 'bold'))
```

## Box plot of MPG from the outcome depending on the type of prosthetics.

```{r}
ggplot(df1) +
  geom_boxplot(aes(x = Upsizing, y = Pre_MAVG_MPG, fill = OS_Event)) +
  labs(x = "Upsizing", y = "MPG") +
  theme_bw() +
  theme(plot.title = element_text(size = 14, hjust = 0.5),
        axis.title = element_text(face = 'bold'))
```

## Сomorbidities

```{r}
# Data preparation 

df1 <- df1 %>% 
  mutate(`Congestive heart failure` = if_else(NYHA_Heart_Fail_Class %in% c(1:4), 1, if_else(is.na(NYHA_Heart_Fail_Class), NA, 0)),
         `Pulmonary hypertension` = Pulm_HTN,
         `Hypertension` = if_else(Art_HTN_Hypto_R == 9, NA, if_else(Art_HTN_Hypto_R %in% c(1:4), 1, 0 )),
         `Coronary artery disease` = if_else(Coronary_Art_Disease == 0, NA, if_else(Coronary_Art_Disease %in% c(2:4), 1, 0 )),
         `Atrial fibrillation` = if_else(Atrial_Fibrillation %in% c(1:3), 1, 0 ),
         `Peripheral artery disease` = if_else(Peripher_Atheroscler %in% c(1:3), 1, 0 ),
         `Endocarditis` = Endocard,
         `Renal Failure` = if_else(Renal_Fail %in% c(2:5), 1, if_else(Renal_Fail == 0, NA, 0 )))



df1 %>% 
  select(Upsizing, `Congestive heart failure`:`Renal Failure`) %>%
  group_by(Upsizing) %>% 
  mutate(across(everything(), \(x) as.factor(x))) %>% 
  summary()
  

```


```{r}
# Converting data to "long" format

df1_comorb_long <- df1 %>% 
  select(Upsizing, `Congestive heart failure`:`Renal Failure`) %>% 
  group_by(Upsizing) %>% 
  pivot_longer(cols = `Congestive heart failure`:`Renal Failure`, names_to = "Feature", values_to = "Value") %>% 
  filter(Upsizing %in% c("Yes", "No")) %>% 
  group_by(Upsizing, Feature) %>% 
  summarise(Count_proc = sum(Value, na.rm = TRUE)/n())


# Distribution of comorbidities in the groups.

ggplot(df1_comorb_long,                         
       aes(x = Feature,
           y = Count_proc,
           fill = Upsizing)) + 
  geom_col() +
  facet_grid(~ Upsizing) +
  coord_flip() +
  scale_y_continuous(labels = percent) +
  labs(x = "Comorbidities", y = "Percent") +
  theme_bw() +
  theme(plot.title = element_text(size = 14, hjust = 0.5),
        axis.title = element_text(face = 'bold'),
        axis.text.x = element_text(angle= 90 , vjust= 0.5 , hjust= 1 )) 

```


```{r}
df1_comorb_long <- df1 %>% 
  select(Upsizing, `Congestive heart failure`:`Renal Failure`) %>% 
  group_by(Upsizing) %>% 
  pivot_longer(cols = `Congestive heart failure`:`Renal Failure`, names_to = "Feature", values_to = "Value") %>% 
  filter(Upsizing %in% c("Yes", "No"))

ggplot(df1_comorb_long,                         
       aes(x = Feature,
           y = Value,
           fill = Upsizing)) + 
  geom_bar(stat = "identity", position = "stack") +
  facet_grid(~ Upsizing) +
  coord_flip() +
  labs(x = "Comorbidities", y = "Count") +
  theme_bw() +
  theme(plot.title = element_text(size = 14, hjust = 0.5),
        axis.title = element_text(face = 'bold'))


```



# Comparison of echocardiography parameters between groups with normal-sized and upsizing
## before surgery

```{r}
df1 <- df1 %>% 
   mutate(Pre_AKI = ifelse(Pre_AKI %in% c(3, 4), "3-4", as.character(Pre_AKI)))

df1 %>% 
  select(Upsizing, Pre_LVEF:Pre_AKI, Pre_PHT) %>% 
  filter(!is.na(Upsizing)) %>% 
  tbl_summary(
    type = all_continuous() ~ "continuous2",
    statistic = all_continuous() ~ c(
      "{mean} ({sd})"
    ),
    by = Upsizing,
    missing = "no",
    label =  c("Pre_LVEF" = "LVEF, %",
              "Pre_LVDd" = "LVDd, cm",
              "Pre_LVDs" = "LVDs, cm",
              "Pre_LVOT" = "LVOT, cm",
              "Pre_PAP" = "PAP, mmHg",
              "Pre_IVSd" = "IVSd, cm",
              "Pre_IVSs" = "IVSs, cm", 
              "Pre_MAVG_MPG" = "MPG, mmHg",
              "Pre_Vmax" = "Vmax, m/sec",
              "Pre_Aort_Valve_Area" = "Aortic valve area, cm2",
              "Pre_AKI" = "Aortic insufficiency",
              "Pre_PHT" = "Pulmonary Hypertension"),
    digits = c(all_continuous() ~ c(1, 1),
               all_categorical() ~ c(0, 1))
  ) %>% 
   add_p(all_continuous() ~t.test) %>% 
   add_q(method = "holm") %>% 
   modify_header(label ~ "**Variable**") %>%
   modify_spanning_header(c("stat_1", "stat_2") ~ "**Upsizing**") %>%
   bold_labels()
```
We use the Holm's method for controlling FWER.

There were no statistically significant differences found between the group with upsizing and the group with a normal-sized prosthesis ( Welch Two Sample t-test, p adj>0.05).


```{r}
#for presentation

table_echo_pre <- df1 %>% 
  select(Upsizing, Pre_LVEF, Pre_MAVG_MPG, Pre_Aort_Valve_Area, Pre_AKI) %>% 
  filter(!is.na(Upsizing)) %>% 
  tbl_summary(
    type = all_continuous() ~ "continuous2",
    statistic = all_continuous() ~ c(
      "{mean} ({sd})"
    ),
    by = Upsizing,
    missing = "ifany",
    label = c("Pre_LVEF" = "LVEF, %",
              "Pre_LVDd" = "LVDd, cm",
              "Pre_LVDs" = "LVDs, cm",
              "Pre_LVOT" = "LVOT, cm",
              "Pre_PAP" = "PAP, mmHg",
              "Pre_IVSd" = "IVSd, cm",
              "Pre_IVSs" = "IVSs, cm", 
              "Pre_MAVG_MPG" = "MPG, mmHg",
              "Pre_Vmax" = "Vmax, m/sec",
              "Pre_Aort_Valve_Area" = "Aortic valve area, cm2",
              "Pre_AKI" = "Aortic insufficiency",
              "Pre_PHT" = "Pulmonary Hypertension"),
    digits = c(all_continuous() ~ c(1, 1),
               all_categorical() ~ c(0, 1))
  ) %>% 
   add_p(all_continuous() ~t.test) %>% 
   add_q(method = "holm") %>% 
   modify_header(label ~ "**Variable**") %>%
   modify_spanning_header(c("stat_1", "stat_2") ~ "**Upsizing**") %>%
   bold_labels()
```

```{r}
table_echo_pre %>% 
  as_gt() %>%
  gt::gtsave(filename = "data/pics/table_echo_pre.png") 
```


## before surgery - follow-up

```{r}
#prepare data
df_echo_pre_fu <- df1 %>% 
  rename(Pre_MAVG = Pre_MAVG_MPG) %>% 
  select(Pre_LVEF:Pre_IVSd, Pre_MAVG:Pre_Aort_Valve_Area, FUEcho_EF:FUEcho_AOF) 

n <- ncol(df_echo_pre_fu)
s1 <- seq(1, n/2)
s2 <- seq(n/2+1, n)

df_echo_pre_fu[paste(names(df_echo_pre_fu)[s1], names(df_echo_pre_fu)[s2], sep="-")] <- df_echo_pre_fu[, s1] - df_echo_pre_fu[, s2]

df_echo_pre_fu <- df_echo_pre_fu %>% 
  select(`Pre_LVEF-FUEcho_EF`:`Pre_Aort_Valve_Area-FUEcho_AOF`)

df2 <- bind_cols(df1, df_echo_pre_fu)
```


```{r}
df2 %>% 
  select(Upsizing, `Pre_LVEF-FUEcho_EF`:`Pre_Aort_Valve_Area-FUEcho_AOF`) %>% 
  filter(!is.na(Upsizing)) %>% 
  tbl_summary(
    type = all_continuous() ~ "continuous2",
    statistic = all_continuous() ~ c(
      "{mean} ({sd})",
      "{median} ({p25}, {p75})",
      "{min}, {max}"
    ),
    by = Upsizing,
    missing = "always",
    digits = c(all_continuous() ~ c(1, 1),
               all_categorical() ~ c(0, 1))
  ) %>% 
   add_p(all_continuous() ~t.test, ) %>% 
   add_q(method = "holm") %>% 
   modify_header(label ~ "**Variable**") %>%
   modify_spanning_header(c("stat_1", "stat_2") ~ "**Upsizing**") %>%
   bold_labels()
```

# Comparison of operation characteristics between groups with normal-sized and upsizing

```{r}
df_sx <- df1 %>% 
  select(Upsizing, Sx_Duration_Min, Sx_Cardiopulm_Bypass_t, Sx_Aort_Clamp_t) %>% 
  filter(!is.na(Upsizing))

df_sx %>% 
  group_by(Upsizing) %>% 
  get_summary_stats(`Sx_Duration_Min`, type = "mean_sd")


#QQ-plot
ggqqplot(df_sx, x = "Sx_Duration_Min", facet.by = "Upsizing")

# Welch's t-test
stat.test <- df_sx %>% 
  t_test(`Sx_Duration_Min` ~ Upsizing) %>% 
  add_xy_position(x = "Upsizing")
stat.test

# Visualization
ggboxplot(
  df_sx, 
  x = "Upsizing", y = "Sx_Duration_Min", 
  ylab = "Duration of the operation, min", xlab = "Upsizing",
  fill = "#ffcc8c"
  ) + 
  labs(subtitle = get_test_label(stat.test, detailed = TRUE)) + 
  stat_pvalue_manual(stat.test, tip.length = 0) 
```

```{r}
ttest<- t.test(df_sx$Sx_Duration_Min ~ df_sx$Upsizing) %>% 
  tidy()
```

The difference in mean Duration of the operation between the standard size group and the upsizing group `r round(ttest$estimate,1)` [`r round(ttest$conf.low,1)` ; `r round(ttest$conf.high,2)`] min. The difference is clinically insignificant.


```{r}
df_sx %>% 
  group_by(Upsizing) %>% 
  get_summary_stats(`Sx_Cardiopulm_Bypass_t`, type = "mean_sd")


# Welch's t-test
stat.test <- df_sx %>% 
  t_test(`Sx_Cardiopulm_Bypass_t` ~ Upsizing) %>% 
  add_xy_position(x = "Upsizing")
stat.test

# Visualization
ggboxplot(
  df_sx, 
  x = "Upsizing", y = "Sx_Cardiopulm_Bypass_t", 
  ylab = "Cardiopulmonary Bypass Time, min", xlab = "Upsizing",
  fill = "#ffcc8c" 
  ) + 
  labs(subtitle = get_test_label(stat.test, detailed = TRUE)) + 
  stat_pvalue_manual(stat.test, tip.length = 0) 
```

```{r}
ttest<- t.test(df_sx$Sx_Cardiopulm_Bypass_t ~ df_sx$Upsizing) %>% 
  tidy()

```
The difference in mean Cardiopulmonary Bypass Time between the standard size group and the upsizing group `r round(ttest$estimate,1)` [`r round(ttest$conf.low,1)` ; `r round(ttest$conf.high,2)`] min. 

```{r}
df_sx %>% 
  group_by(Upsizing) %>% 
  get_summary_stats(`Sx_Aort_Clamp_t`, type = "mean_sd")


# Welch's t-test
stat.test <- df_sx %>% 
  t_test(`Sx_Aort_Clamp_t` ~ Upsizing) %>% 
  add_xy_position(x = "Upsizing")
stat.test

# Visualization
ggboxplot(
  df_sx, 
  x = "Upsizing", y = "Sx_Aort_Clamp_t", 
  ylab = "Aortic clamp time, min", xlab = "Upsizing",
  fill = "#ffcc8c" 
  ) + 
  labs(subtitle = get_test_label(stat.test, detailed = TRUE)) + 
  stat_pvalue_manual(stat.test, tip.length = 0) 
```


`
```{r}
ttest<- t.test(df_sx$Sx_Aort_Clamp_t ~ df_sx$Upsizing) %>% 
  tidy()

```

The difference in mean Aortic clamp time between the standard size group and the upsizing group `r round(ttest$estimate,1)` [`r round(ttest$conf.low,1)` ; `r round(ttest$conf.high,2)`] min.


## Summary table of temporal characteristics of the operation

```{r}
df_sx <- df1 %>% 
  select(Upsizing, Sx_Duration_Min, Sx_Cardiopulm_Bypass_t, Sx_Aort_Clamp_t) %>% 
  filter(!is.na(Upsizing))

df_sx %>% 
  tbl_summary(
    type = all_continuous() ~ "continuous2",
    statistic = all_continuous() ~ c(
      "{mean} ({sd})",
      "{median} ({p25}, {p75})",
      "{min}, {max}"
    ),
    by = Upsizing,
    missing = "no",
    label = c("Sx_Duration_Min" = "Duration of the operation, min",
              "Sx_Cardiopulm_Bypass_t" = "Duration of cardiopulmonary bypass, min",
              "Sx_Aort_Clamp_t" = "Aortic clamping time, min"),
    digits = c(all_continuous() ~ c(1, 1),
               all_categorical() ~ c(0, 1))
  ) %>% 
   add_p(all_continuous() ~t.test) %>%
   add_q(method = "holm") %>% 
   modify_header(label ~ "**Variable**") %>%
   modify_spanning_header(c("stat_1", "stat_2") ~ "**Upsizing**") %>%
   bold_labels()
```


# MPG (pre-post) vs Upsizing (linear regression)

```{r}
df1 <- df1 %>% 
  mutate(`Pre MPG` = Pre_MAVG_MPG)

```

**MPG post linear model**

```{r}
df1_fit_MPG_post_crude <- lm(`Post_MAVG` ~ Upsizing, df1)

tbl_regression(df1_fit_MPG_post_crude, intercept = TRUE) %>% 
  add_significance_stars(hide_ci = FALSE, hide_p = FALSE) %>% 
  add_glance_source_note()
```

**MPG post linear model adj**

```{r}
df1_fit_MPG_post_adj <- lm(`Post_MAVG` ~ `Pre MPG` + Upsizing + Prosthesis_Anat_Size, df1)

tbl_regression(df1_fit_MPG_post_adj, intercept = TRUE) %>% 
  add_significance_stars(hide_ci = FALSE, hide_p = FALSE) %>% 
  add_glance_source_note()
```

```{r}
vif(df1_fit_MPG_post_adj)
#The residuals have equal variance (homoscedasticity)
```

```{r}
#Diagnostic plots
autoplot(df1_fit_MPG_post_adj)
```


```{r}
# correction for heteroscedasticity
#robust_fit <- coeftest(df1_fit_MPG_post_adj, vcov = vcovHC, type = "HC4")
#robust_fit
```

**Summary table for MPG (pre-post)**

```{r}
mod_summary_MPG_post <- modelsummary::modelsummary(
  list("MPG (post) crude " = df1_fit_MPG_post_crude,
       "MPG (post) adj." = df1_fit_MPG_post_adj),
  statistic = NULL,
  fmt = 1,
  coef_omit = "Intercept",
  estimate =  "{estimate} {stars}[{conf.low}, {conf.high}]",
 # stars = TRUE,
  gof_map = "nobs",
  output="gt")

mod_summary_MPG_post
  
```

```{r}
gt::gtsave(mod_summary_MPG_post, "data/pics/mod_summary_MPG_post.png")
```

# EF (pre-post) linear model

**EF post linear model**

```{r}
df1_fit_EF_post_crude <- lm(Post_LVEF ~ Upsizing, df1)

tbl_regression(df1_fit_EF_post_crude , intercept = TRUE) %>% 
  add_significance_stars(hide_ci = FALSE, hide_p = FALSE) %>% 
  add_glance_source_note()
```

**EF post linear model adj**

```{r}
df1_fit_EF_post_adj <- lm(Post_LVEF ~ Pre_LVEF + Upsizing + Prosthesis_Anat_Size, df1)

tbl_regression(df1_fit_EF_post_adj, intercept = TRUE) %>% 
  add_significance_stars(hide_ci = FALSE, hide_p = FALSE) %>% 
  add_glance_source_note()
```

```{r}
autoplot(df1_fit_EF_post_adj)
```


**Summary table for EF (pre-post)**

```{r}
mod_summary_EF_post <- modelsummary::modelsummary(
  list("EF (post) crude " = df1_fit_EF_post_crude,
       "EF (post) adj." = df1_fit_EF_post_adj),
  statistic = NULL,
  fmt = 1,
  coef_omit = "Intercept",
  estimate =  "{estimate} {stars}[{conf.low}, {conf.high}]",
 # stars = TRUE,
  gof_map = "nobs",
  output="gt")

mod_summary_EF_post
  
```

```{r}
gt::gtsave(mod_summary_EF_post, "data/pics/mod_summary_EF_post.png")
```

# MPG (pre/follow-up) vs Upsizing

```{r}
df1 <- df1 %>% 
  mutate(`Time, days (fu-sx)` = as.numeric(ymd(FUEcho_Date) - ymd(Sx_Date)))

#checking the dates 

sum(ymd(df1$FUEcho_Date)<ymd(df1$Sx_Date), na.rm = TRUE)

```

```{r}
ggpairs(
  df1 %>% 
  dplyr::select(FUEcho_MPG, `Pre MPG`, `Time, days (fu-sx)`, Prosthesis_Anat_Size, Upsizing), 
  upper = list(continuous = wrap("points",size = 0.5),
               disrete = "blank",
               combo = wrap("points", size = 0.5)),
  lower = list(continuous = "cor",
               discrete = "count",
               combo = wrap("box_no_facet", outlier.size = 0.5)),
  diag = list(continuous = "barDiag",
              discrete = "barDiag"),
  showStrips = TRUE, progress = FALSE) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


## Crude

**MPG follow-up linear model**

```{r}
summary(df1$`MPG diff pre fu`)

df1_fit_FUEcho_MPG_crude <- lm(`FUEcho_MPG` ~ Upsizing, df1)

tbl_regression(df1_fit_FUEcho_MPG_crude, intercept = TRUE) %>% 
  add_significance_stars(hide_ci = FALSE, hide_p = FALSE) %>% 
  add_glance_source_note()
```

## Adjusted

```{r}
df1_FUEcho_MPG_adj <- lm(`FUEcho_MPG` ~ `Pre MPG` + Upsizing + `Time, days (fu-sx)` + Prosthesis_Anat_Size, df1)

tbl_regression(df1_FUEcho_MPG_adj, intercept = TRUE) %>% 
  add_significance_stars(hide_ci = FALSE, hide_p = FALSE) %>% 
  add_glance_source_note()
```

```{r}
vif(df1_FUEcho_MPG_adj)
```

```{r}
#Diagnostic plots
autoplot(df1_FUEcho_MPG_adj)
```

**Summary table for MPG (pre-follow-up)**

```{r}
mod_summary_MPG <- modelsummary::modelsummary(
  list("MPG (fu) crude " = df1_fit_FUEcho_MPG_crude,
       "MPG (fu) adj." = df1_FUEcho_MPG_adj),
  statistic = NULL,
  fmt = 1,
  coef_omit = "Intercept",
  estimate =  "{estimate} {stars}[{conf.low}, {conf.high}]",
 # stars = TRUE,
  gof_map = "nobs",
  output="gt")

mod_summary_MPG
  
```


```{r}
gt::gtsave(mod_summary_MPG, "data/pics/mod_summary_MPG.png")
```


# EF (pre/follow-up)

## Crude

**EF follow-up linear model**

```{r}
df1_fit_FUEcho_EF_crude <- lm(`FUEcho_EF` ~ Upsizing, df1)

tbl_regression(df1_fit_FUEcho_EF_crude, intercept = TRUE) %>% 
  add_significance_stars(hide_ci = FALSE, hide_p = FALSE) %>% 
  add_glance_source_note()
```

## Adjusted

```{r}
df1_fit_FUEcho_EF_adj <- lm(`FUEcho_EF` ~ `Pre_LVEF` + Upsizing + `Time, days (fu-sx)` + Prosthesis_Anat_Size, df1)

tbl_regression(df1_fit_FUEcho_EF_adj, intercept = TRUE) %>% 
  add_significance_stars(hide_ci = FALSE, hide_p = FALSE) %>% 
  add_glance_source_note()
```

```{r}
autoplot(df1_fit_FUEcho_EF_adj)
```

**Summary table for EF (pre-follow-up)**

```{r}
mod_summary_EF <- modelsummary::modelsummary(
  list("EF (fu) crude " = df1_fit_FUEcho_EF_crude,
       "EF (fu) adj." = df1_fit_FUEcho_EF_adj),
  statistic = NULL,
  fmt = 1,
  coef_omit = "Intercept",
  estimate =  "{estimate} {stars}[{conf.low}, {conf.high}]",
 # stars = TRUE,
  gof_map = "nobs",
  output="gt")

mod_summary_EF
  
```

```{r}
gt::gtsave(mod_summary_EF, "data/pics/mod_summary_EF.png")
```