---
title: "Survival analysis and table 0.1"
output: html_document
date: "2024-01-09"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readxl)
library(survival)
library(survminer)
library(psych)
library(PerformanceAnalytics)
library(tidyverse)
library(flextable)
library(gtsummary)
library(pec)
library(car)
library(forester)
library(casebase)
# install.packages("adjustedCurves")
library(adjustedCurves)
library(splines)
library(mice)
```

## Loading, checking and consolidating data
```{r}
#The dates in the table have been manually corrected. Where there was only a year, the middle of the year is set
#The value "unbekannt" is placed in a separate column to make it easier to impute values further
df_date <- read_xlsx("data/raw/Epic_Supra_dates_v2.xlsx", na = "")

rename <- read.table(file = 'data/raw/Column_data_Renamer_v2.tsv', sep = '\t', header = TRUE)

str(df_date)

# Convert to vector column English_Column_Name_Short for rename
English_Column_Name_Short <- as.vector(rename$English_Column_Name_Short)

# Rename columns names in df_read_excel with vector English_Column_Name_Short
df_date_en <- df_date %>% 
  rename_with(~English_Column_Name_Short, everything())
  
# str(df_date)
# summary(df_date)

# Loading other data
df1_no_date <- read_csv("data/interim/df1_no_date.csv", na = "")

# Joining two tables
df <- df_date_en %>% full_join(df1_no_date, by = c("Case_Num" = "Case_Num"))

# str(df)
# summary(df)

```


Let's impute the data where STERBEDAT = "unbekant"Let's count the last visit as the last of the dates (reoperation, lastfu, fueсho and death)
```{r}
df <- df %>% 
  mutate(Last_FU_upd = pmax(Last_FU, REOP_DAT, FUEcho_Date, OS_Date, na.rm = TRUE))
summary(df$Last_FU_upd)
```


Check:
1. Are there any patients whose date of death is less than the date of their last visit?
2. Are there any patients with the date of the last foluap before surgery?
3. Are there any patients we don’t know about the fact of death who do not have FollowUp?
Let's look at these patients:

```{r}
df <- df %>% 
  mutate(Date_check = case_when(OS_Date < Last_FU_upd - 86400 ~ "Fail",
                                Sx_Date > Last_FU_upd ~ "Fail", 
                                is.na(Last_FU_upd) & OS_Event == 0 ~ "Fail",
                                TRUE ~ "OK"))
         
df %>% 
  filter(Date_check == "Fail") %>% 
  select(c("Case_Num", "OS_Event", "Sx_Date", "OS_Date", "Last_FU_upd", "Date_check"))
```

We exclude patients for whom it is impossible to determine the date of the  FollowUp
```{r}
df_filter <- df %>% 
  filter(Date_check == "OK")
```


Let's find the maximum date, which we will take as the database closure date
```{r}
df_closing_date <- max(df_filter$Last_FU_upd, na.rm = TRUE)
df_closing_date
```


Let's calculate the time until death and impute the data to those whose death we know about, but do not know the date

```{r}
#Calculation of duration between known dates of death and dates of surgery
df_filter <- df_filter %>% 
  mutate(dur_SX_OS = OS_Date - Sx_Date) 

median_dur_if_dead <- median(df_filter$dur_SX_OS, na.rm = TRUE)
as.numeric(median_dur_if_dead)/86400
```


Where there is no last visit and the date of death is unknown, we impute the median time to death, provided that the patient is known to have died.
```{r}
df_filter <- df_filter %>% 
  mutate(dur_SX_OS = if_else(OS_Date_unknown == 1 & is.na(Last_FU_upd) & is.na(dur_SX_OS), median_dur_if_dead, dur_SX_OS))
```


Where there is a last visit, but the date of death is unknown, we substitute the midpoint of the time between the patient’s last visit and the “closing of the database” (the most recent visit of all)
```{r}
df_filter <- df_filter %>% 
  mutate(dur_SX_OS = if_else(OS_Date_unknown == 1 & !is.na(Last_FU_upd) & is.na(dur_SX_OS), (df_closing_date - Last_FU_upd)/2, dur_SX_OS))

df_filter$dur_SX_OS
```


Now let’s check whether all situations can be processed in this way
```{r}
sum(df_filter$OS_Date_unknown == 1 & is.na(df_filter$dur_SX_OS), na.rm = TRUE)
```

## Preparing data for survival analysis


The observation statute is already there, the variable "OS_Event"
It is necessary to calculate the duration of observation for each subject

Let's calculate the duration only for those who are not dead, because for the dead it has already been calculated
```{r}
# df_filter$Last_FU_upd
# df_filter$Sx_Date
df_filter <- df_filter %>% 
  mutate(dur_SX_Last_FU = Last_FU_upd - Sx_Date)

filter(df_filter, dur_SX_Last_FU < 0) %>% 
   select(c("Case_Num", "OS_Event", "Sx_Date", "OS_Date", "Last_FU_upd", "Date_check"))
```

Combine the duration to death with the duration to last follow-up
```{r}
df_filter <- df_filter %>% 
  mutate(DUR = if_else(!is.na(dur_SX_OS), dur_SX_OS, NA)) %>% 
  mutate(DUR = if_else(is.na(DUR) & !is.na(dur_SX_Last_FU), dur_SX_Last_FU, DUR)) %>% 
  mutate(DUR = ceiling(as.numeric(DUR) / 86400))

summary(df_filter$DUR)
df_filter$DUR

summary(df_filter$Sx_Aort_Clamp_t)
```


Save the dataset with patients for whom the outcome/duration is known
```{r}
# str(df_filter)
write.csv(df_filter, "data/interim/df_filter_surv.csv", row.names = FALSE) # Без изменений после загрузки из excel
```


## Baseline values of demographic and anthropometric characteristics

Let's select the variables we are interested in
```{r}
df_surv_all <- df_filter %>% 
  select("Case_Num", "Age", "BMI", "Gender", "STS", "Prosthesis_Anat_Aort_Valve",
         "Pre_Bicuspid", "Prosthesis_Anat_Size", "Sx_Date", "Upsizing", "OS_Event", "DUR") %>% 
  mutate(Prosthesis_Anat_Size = as.numeric(Prosthesis_Anat_Size))
```


The value of characteristics at time point 0 in the groups of known upsizing and unknown upsizing
```{r}
#df_date_surv <- df_date %>% 
#  mutate(Upsizing = as.factor(Upsizing))  %>% 
#  mutate(Upsizing = if_else(is.na(Upsizing), "NA", "Known")) %>% 
#  filter(!is.na(DUR))

df_surv_all %>% 
  select(-c("Case_Num")) %>% 
  tbl_summary(by = Upsizing) %>% 
  add_p()
```


Value of characteristics at time point 0 only in groups of known upsizing
```{r}
df_surv_known_tmp <- df_filter %>% 
  select("Case_Num", "Age", "BMI", "Gender", "NYHA_Heart_Fail_Class", "STS", "Prosthesis_Anat_Aort_Valve", "Pre_Bicuspid", "Prosthesis_Anat_Size", "Sx_Date", "Upsizing", "OS_Event", "DUR", "Sx_Urgency", "Sx_Surgeon", "Sx_Urgency") %>% 
  mutate(Prosthesis_Anat_Size = as.numeric(Prosthesis_Anat_Size),
         Upsizing = as.factor(if_else(Upsizing == "NA", NA, Upsizing)),
         #Sx_Aort_Clamp_t = if_else(Sx_Aort_Clamp_t == 0, median(Sx_Aort_Clamp_t), Sx_Aort_Clamp_t)
        ) %>% 
  filter(!is.na(Upsizing))

df_surv_known_tmp %>% 
  select(-c("Case_Num")) %>% 
  tbl_summary(by = Upsizing) %>% 
  add_p()
```


Formatted table

```{r}
df_surv_known <- df_surv_known_tmp %>% 
  select(-Pre_Bicuspid) %>% 
  add_count(Sx_Surgeon) %>% 
  mutate(Gender = as.factor(if_else(Gender == 1, "male", "female")),
         Year_of_surgery_after_init = as.numeric(Sx_Date - min(Sx_Date, na.rm = TRUE))/31688100,
         Upsizing = as.factor(if_else(Upsizing == 1, "UP_size", "Anatomical_Size")),
         NYHA_Heart_Fail_Class  = as.factor(if_else(NYHA_Heart_Fail_Class <3, "0-2", "3-4") ),
         Urgency = as.factor(if_else(Sx_Urgency == 1, "Elective surgery", "Urgent surgery")),
         Surgeon = ifelse(n > 100, Sx_Surgeon, "other surgeons"),
         Prosthesis_Anat_Aort_Valve = as.factor(case_when(Prosthesis_Anat_Aort_Valve == 0 ~ "3x",
                                                          Prosthesis_Anat_Aort_Valve == 1 ~ "2x",
                                                          Prosthesis_Anat_Aort_Valve == 2 ~ "3x")),
         Event_death = OS_Event,
        time_year = DUR/365.25) %>% 
  mutate(Surgeon = case_when(Surgeon == "Ltd. OÄ Dr. med. G. Färber" ~ "GF",
                             Surgeon == "OA Dr. med. M. Diab" ~ "MD",
                             Surgeon == "OA Dr. med. T. Sandhaus" ~ "TS",
                             Surgeon == "PD Dr. med. M. Richter" ~ "MR",
                             Surgeon == "Prof. Dr. med. T. Doenst" ~ "TD",
                             Surgeon == "other surgeons" ~ "other"),
          Urgency = as.factor(if_else(Sx_Urgency == 1, "Elective surgery", "Urgent surgery")),) %>% 
  select(c("Age", "BMI", "Gender", "NYHA_Heart_Fail_Class", "STS", "Prosthesis_Anat_Aort_Valve", "Urgency", "Prosthesis_Anat_Size",  "Surgeon", "Upsizing", "time_year", "Event_death", "OS_Event")) 

df_surv_known %>%
  select(-c("OS_Event", "time_year", "Event_death")) %>% 
  tbl_summary(by = Upsizing) %>% 
  add_p(test = list(all_continuous() ~ "t.test"))
```


## Relationship of the main variables of the analysis


```{r, warning=FALSE}

library(GGally)
ggpairs(df_surv_known %>% select(-c("OS_Event", "time_year")), 
  upper = list(continuous = wrap("points", alpha = 0.5, size = 1),
               combo = wrap("points", alpha = 0.5, size = 1),
               disrete = "blank"),
  lower = list(continuous = "cor",
               discrete = "count",
               combo = wrap("box_no_facet", outlier.size = 0.5)),
  diag = list(continuous = "barDiag",
              discrete = "barDiag"),
  showStrips = TRUE, progress = FALSE) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        panel.grid.minor = element_blank(),
        strip.placement = "outside",
        strip.background = element_rect(color = "white", fill = "#EFEBE9"),
        strip.text = element_text(size = 6, face = "bold"))
```

## Survival analysis


Crude model KM plot
```{r}
df_surv_known_tmp2 <-  df_surv_known_tmp %>% 
mutate(Upsizing = if_else(Upsizing == "1", "Yes", "No"))

surv_object <- Surv(time = df_surv_known$time_year, event = df_surv_known_tmp2$OS_Event)

fit_crude_KM <- survfit(surv_object ~ Upsizing, data = df_surv_known_tmp2)
fit_crude <- coxph(surv_object ~ Upsizing, data = df_surv_known_tmp2)


q1 <- quantile(fit_crude_KM, probs = c(0.25, 0.75),
              conf.int = TRUE)
as.data.frame(q1)

p1 <- ggsurvplot(fit_crude_KM,
                title = "survival plot",
                conf.int = TRUE,
                risk.table = TRUE,
                tables.height = 0.2,
                pval = TRUE, 
                pval.coord = c(750, 0.7),
                log.rank.weights = "1",
                xlab = "Time, year",
                ylim = c(0.5, 1))

p1
fit_crude

tbl_crude <- tbl_regression(fit_crude, exponentiate = TRUE)
tbl_crude
```

```{r}
test.ph <- cox.zph(fit_crude)
ggcoxzph(test.ph)
concordance(fit_crude)
```

Full model
```{r}
fit_full <- coxph(surv_object ~ Upsizing + Prosthesis_Anat_Size + Age + Surgeon + BMI + Gender + log10(STS+1) + NYHA_Heart_Fail_Class + Prosthesis_Anat_Aort_Valve,
                   data = df_surv_known, x = TRUE)

fit_full

tbl_full <- tbl_regression(fit_full, exponentiate = TRUE)
tbl_full
```


```{r}
cox.zph(fit_full)
test.ph <- cox.zph(fit_full)
ggcoxzph(test.ph)
concordance(fit_full)
vif(fit_full)

```
Date of surgery did not affect outcomes.
Adding surgeons improved the statistical significance of upsyzine. And there are at least a few surgeons between whom there are statistically significant differences




Two minimum reasonable models
```{r}
fit_mini1 <- coxph(surv_object ~  Upsizing + Prosthesis_Anat_Size + Age,
                   data = df_surv_known)

fit_mini2 <- coxph(surv_object ~  Upsizing + Prosthesis_Anat_Size + Age  + Surgeon,
                   data = df_surv_known)

tbl1 <- tbl_regression(fit_mini1, exponentiate = TRUE)
tbl2 <- tbl_regression(fit_mini2, exponentiate = TRUE)

anova(fit_mini1, fit_mini2)

```


Test minimal model
```{r}
test.ph <- cox.zph(fit_mini2)
ggcoxzph(test.ph)
concordance(fit_mini2)
```


Optimal model
```{r}
fit_optimal <- coxph(surv_object ~  Upsizing + Prosthesis_Anat_Size  + Age + Surgeon + log10(STS+1),
                   data = df_surv_known)

tbl_optimal <- tbl_regression(fit_optimal, exponentiate = TRUE)
tbl_optimal
```

```{r}

tbl_merge(list(tbl_crude, tbl2, tbl_full), tab_spanner = c("Univarative", "Adjustment_1", "Adjasment_full"))
```


Let's test the model in more detail
```{r}

cox.zph(fit_full)
test.ph <- cox.zph(fit_full)
ggcoxzph(test.ph)
concordance(fit_full)
concordance(fit_mini2)
vif(fit_full)
anova(fit_full, fit_mini2)
ggcoxdiagnostics(fit_full, type = c("martingale"))
ggcoxdiagnostics(fit_full, type = c("deviance"))
ggcoxdiagnostics(fit_full, type = c("score"))
ggcoxdiagnostics(fit_full, type = c("schoenfeld"))
ggcoxdiagnostics(fit_full, type = c("dfbeta"))
ggcoxdiagnostics(fit_full, type = c("dfbetas"))
ggcoxdiagnostics(fit_full, type = c("scaledsch"))
# ggcoxdiagnostics(fit_covariance, type = c("partial"))
ggcoxdiagnostics(fit_full, type = "dfbetas", point.size = 0, hline.col = "black",
sline.col = "black") + geom_bar(stat = "identity")
```



Building a Forrest Raft for a model with categories

```{r}
df_surv_known <- df_surv_known %>% 
  mutate(Age__ = if_else(Age < 70, "< 70", "70+"),
         BMI__ = if_else(BMI < 30, "< 30", "30+"),
         Gender__ = Gender,
         STS__ = if_else(STS < 3, "< 3", "3+"),
         Prosthesis_Anat_Size__ = if_else(Prosthesis_Anat_Size < 26, "< 26", "26+"),
         NYHA_Heart_Fail_Class__ = NYHA_Heart_Fail_Class)

surv_object <- Surv(time = df_surv_known$time_year, event = df_surv_known$OS_Event)

fit_covariance <- coxph(surv_object ~ Age__ +  BMI__ + Gender__ + STS__ + Prosthesis_Anat_Aort_Valve + Prosthesis_Anat_Size__ + Upsizing,
                  data = as.data.frame(df_surv_known))

broom::tidy(fit_covariance, conf.int = TRUE)

cox.zph(fit_covariance)
ggforest(fit_covariance)
```


Forrest raft construction for the model within the categories
```{r}

perform_cox_analysis <- function(df, subgroup_var, subgroup_level) {
  # Filter for subgroup
  df_subgroup <- df %>% filter(get(subgroup_var) == subgroup_level)

  # Build the model formula excluding the subgroup_var variable
  covariates <- c("Age", "BMI", "Gender", "STS", "Prosthesis_Anat_Aort_Valve", "Prosthesis_Anat_Size", "Upsizing")
  covariates <- covariates[covariates != subgroup_var] # remove the current grouping variable from the list of covariates
  formula <- as.formula(paste("Surv(time_year, OS_Event) ~", paste(covariates, collapse = " + ")))

  # Cox model for the subgroup with a new formula
  cox_model <- coxph(formula, data = df_subgroup)
  cox_summary <- summary(cox_model)
  
  # Definition of confidence intervals
  confint_cox <- confint(cox_model)
  
  coef_name <- grep("Upsizing", rownames(cox_summary$coefficients), value = TRUE)

  # Obtaining coefficients and confidence intervals
  hr <- cox_summary$coefficients[coef_name, "coef"]
  lower_ci <- confint_cox[coef_name, 1]
  upper_ci <- confint_cox[coef_name, 2]
  
  upsizing_counts <- df_subgroup %>% 
    group_by(Upsizing) %>% 
    summarize(count = n()) %>% 
    pivot_wider(names_from = Upsizing, values_from = count)

  # Returning the results
tibble(
  Subgroup = paste(subgroup_var, subgroup_level),
   Up_size_Count = upsizing_counts$`UP_size`, # Assign the calculated values to the appropriate column
  Anathomical_size_Count = upsizing_counts$`Anatomical_Size`, #  Assign the calculated values to the appropriate column
  HR = exp(hr), # We take the exponent of the coefficient for HR
  HR_lower_CI = exp(confint_cox[coef_name, 1]), # ТWe also take the exponent for the lower CI
  HR_upper_CI = exp(confint_cox[coef_name, 2]), # And for the upper CI
  P_value = cox_summary$coefficients[coef_name, "Pr(>|z|)"]
  )

  }
  
  # We get a list of variables and their levels to be analysed
subgroups <- list(
  "Age__" = c("< 70", "70+"),
  "BMI__" = c("< 30", "30+"),
  "Gender__" = c("male", "female"),
  "STS__" = c("< 3", "3+"),
  "Prosthesis_Anat_Size__" = c("< 26", "26+"),
    "NYHA_Heart_Fail_Class__" = c("0-2", "3-4")
)

# Apply the perform_cox_analysis function for each variable and each level
results <- map_df(names(subgroups), ~{
  subgroup_var <- .x
  subgroup_levels <- subgroups[[subgroup_var]]
  
  # For each level in a subgroup
  map_dfr(subgroup_levels, ~perform_cox_analysis(df_surv_known, subgroup_var, .x), .id = "Subgroup_level")
}, .id = "Subgroup_var")

results


# We construct a summary Cox regression model on all patients
combined_cox_model <- coxph(Surv(time_year, OS_Event) ~ Age + BMI + Gender + log10(STS+1) + Prosthesis_Anat_Aort_Valve + Prosthesis_Anat_Size  + Upsizing + NYHA_Heart_Fail_Class,
                            data = df_surv_known)
combined_cox_summary <- summary(combined_cox_model)
combined_confint_cox <- confint(combined_cox_model)
combined_coef_name <- grep("Upsizing", rownames(combined_cox_summary$coefficients), value = TRUE)

# We obtain the coefficient and confidence intervals for the "total" model
combined_hr <- combined_cox_summary$coefficients[combined_coef_name, "coef"]
combined_lower_ci <- combined_confint_cox[combined_coef_name, 1]
combined_upper_ci <- combined_confint_cox[combined_coef_name, 2]
combined_upsizing_counts <- df_surv_known %>% 
  group_by(Upsizing) %>% 
  summarize(count = n()) %>% 
  pivot_wider(names_from = Upsizing, values_from = count)

# Add the results of the summary model to the results table
summary_results <- tibble(
  Subgroup = "All Patients",
  HR = exp(combined_hr),
  HR_lower_CI = exp(combined_lower_ci),
  HR_upper_CI = exp(combined_upper_ci),
  P_value = combined_cox_summary$coefficients[combined_coef_name, "Pr(>|z|)"]
)
#You need to add: Up_size_Count and Anathomical_size_Count, based on your previous counting logic
summary_results$Up_size_Count <- combined_upsizing_counts$`UP_size`
summary_results$Anathomical_size_Count <- combined_upsizing_counts$`Anatomical_Size`

# We combine the results of the subgroups with the results of the summary model
final_results <- bind_rows(summary_results, results) %>% 
  select(Subgroup, Up_size_Count, Anathomical_size_Count, HR, HR_lower_CI, HR_upper_CI, P_value)

final_results

# forestplot(labeltext = final_results$Subgroup,
#           mean = final_results$HR,
#           lower = final_results$HR_lower_CI,
 #          upper = final_results$HR_upper_CI,
  #         xlab = "Hazard Ratio",
   #        line.margin = 0.15)
```


Let us construct a Forest plot of upsizing in the subgroups of the study. In this way we can understand the interaction of patients with upsizing

```{r}
# devtools::install_github("rdboyes/forester")


# Removing "_<level>" from subgroup names to get unique subgroup names
subgroup_names <- unique(sub("__.+$", "", final_results$Subgroup))

# Removing "All Patients" from subgroup names to create separate rows
subgroup_names <- subgroup_names[subgroup_names != "All Patients"]

# Create rows with subgroups where all values except 'Subgroup' are NA
subgroup_rows <- tibble(
  Subgroup = subgroup_names,
  Group = subgroup_names,
  HR = NA_real_,
  HR_lower_CI = NA_real_,
  HR_upper_CI = NA_real_,
  P_value = NA_real_,
  Up_size_Count = NA_integer_,
  Anathomical_size_Count = NA_integer_
)

# Split subgroup names in `final_results` into group and subgroups
final_results_2 <- final_results %>%
  mutate(
    Group = if_else(grepl("_", Subgroup), sub("__.*", "", Subgroup), NA_character_),
    Subgroup = if_else(grepl("_", Subgroup), sub(".*_", "", Subgroup), Subgroup)
  )

# Insert rows with subgroup names 
final_with_subgroups <- bind_rows(subgroup_rows, final_results_2) %>%
  arrange(Group, is.na(Group), desc(Subgroup))

# Let's format the 'Subgroup' for use in forester
final_with_subgroups <- final_with_subgroups %>%
  mutate(Subgroup = if_else(!is.na(Group), paste("   ", Subgroup), Subgroup))

# Now final_with_subgroups contains rows with subgroup names and rows with subgroups

# Preparing the left side of the table for Forester
left_side_data <- final_with_subgroups %>%
  mutate(Subgroup = if_else(is.na(HR), Subgroup, paste0("   ", Subgroup))) %>% 
  select(Subgroup, Up_size_Count, Anathomical_size_Count) %>% 
  rename(Upsizing = Up_size_Count, Anat_size = Anathomical_size_Count)

# Use forester to create a graph with a table
forester_plot <- forester(
  left_side_data = left_side_data,
  estimate = final_with_subgroups$HR,
  ci_low = final_with_subgroups$HR_lower_CI,
  ci_high = final_with_subgroups$HR_upper_CI,
  display = TRUE, 
  null_line_at = 1,
  estimate_col_name = "HR (95CI)"
)
```

```{r, warning = FALSE}
df_surv_all <- df_filter %>% 
  select("Case_Num", "Age", "BMI", "Gender", "NYHA_Heart_Fail_Class", "STS", "Prosthesis_Anat_Aort_Valve", "Pre_Bicuspid", "Prosthesis_Anat_Size", "Sx_Date", "Upsizing", "OS_Event", "DUR", "Sx_Urgency", "Sx_Surgeon") %>% 
  mutate(Prosthesis_Anat_Size = as.numeric(Prosthesis_Anat_Size),
         Upsizing = if_else(Upsizing == "NA", "Unknown", "Known"),
         #Sx_Aort_Clamp_t = if_else(Sx_Aort_Clamp_t == 0, median(Sx_Aort_Clamp_t), Sx_Aort_Clamp_t)
        ) %>% 
   select(-Pre_Bicuspid) %>% 
  add_count(Sx_Surgeon) %>% 
  mutate(BMI = if_else(is.na(BMI), mean(BMI, na.rm=TRUE), BMI),
         Gender = as.factor(if_else(Gender == 1, "male", "female")),
         Year_of_surgery_after_init = as.numeric(Sx_Date - min(Sx_Date, na.rm = TRUE))/31688100,
         NYHA_Heart_Fail_Class  = as.factor(if_else(NYHA_Heart_Fail_Class <3, "0-2", "3-4") ),
         Urgency = as.factor(if_else(Sx_Urgency == 1, "Elective surgery", "Urgent surgery")),
         Surgeon = ifelse(n > 100, Sx_Surgeon, "other surgeons"),
         Prosthesis_Anat_Aort_Valve = as.factor(case_when(Prosthesis_Anat_Aort_Valve == 0 ~ "3x",
                                                          Prosthesis_Anat_Aort_Valve == 1 ~ "2x",
                                                          Prosthesis_Anat_Aort_Valve == 2 ~ "3x")),
         Event_death = OS_Event,
        time_year = DUR/365.25) %>% 
  mutate(Surgeon = case_when(Surgeon == "Ltd. OÄ Dr. med. G. Färber" ~ "GF",
                             Surgeon == "OA Dr. med. M. Diab" ~ "MD",
                             Surgeon == "OA Dr. med. T. Sandhaus" ~ "TS",
                             Surgeon == "PD Dr. med. M. Richter" ~ "MR",
                             Surgeon == "Prof. Dr. med. T. Doenst" ~ "TD",
                             Surgeon == "other surgeons" ~ "other")) %>% 
  select(c("Age", "BMI", "Gender", "NYHA_Heart_Fail_Class", "STS", "Prosthesis_Anat_Aort_Valve", "Prosthesis_Anat_Size",  "Surgeon", "Upsizing", "Year_of_surgery_after_init", "time_year", "Event_death", "OS_Event")) 

df_surv_all %>%
  select(-c("OS_Event", "time_year", "Event_death")) %>% 
  tbl_summary(by = Upsizing) %>% 
  add_p(test = list(all_continuous() ~ "t.test"))
```


Dynamics of HR deaths over time
```{r}
haz <- fitSmoothHazard(OS_Event ~ ns(time_year, df = 3) + log10(STS+1) + Prosthesis_Anat_Size + Upsizing,
                   data = df_surv_known, time = "time_year")

gg_object <- plot(haz,
                  hazard.params = list(xvar = "time_year",
                                       by = "Upsizing",
                                       alpha = 0.20, # 80% CI
                                       ylab = "Hazard",
                                       gg = TRUE)) 
gg_object +
  theme_bw()
```


```{r}
fit_covariance <- coxph(surv_object ~ log10(STS + 1) + Prosthesis_Anat_Aort_Valve + Upsizing,
                   data = df_surv_known)

fit_covariance2 <- coxph(surv_object ~ log10(STS + 1) + Prosthesis_Anat_Aort_Valve,
                   data = df_surv_known)

tbl_regression(fit_covariance, 
              exponentiate = TRUE)

test.ph <- cox.zph(fit_covariance)
ggcoxzph(test.ph)
concordance(fit_covariance)
vif(fit_covariance)
anova(fit_covariance, fit_covariance2)

```


# Multivariate Imputation by Chained Equations (MICE)
```{r eval=FALSE, include=FALSE}
df_filter%>% 
select(Case_Num, Age, Gender, Height, Weight, NYHA_Heart_Fail_Class, Prosthesis_Anat_Size, Prosthesis_Size, Pre_LVOT, DUR, BMI, Prosthesis_Anat_Aort_Valve, Sx_Surgeon, Upsizing, Pre_LVOT, OS_Event, STS, Sx_Urgency, Sx_Date) %>% 
   add_count(Sx_Surgeon) %>% 
   mutate(Prosthesis_Anat_Size = as.numeric(Prosthesis_Anat_Size),
          Sx_Date = as.numeric(Sx_Date - min(Sx_Date, na.rm = TRUE))/31688100,
         Gender = as.factor(if_else(Gender == 1, "male", "female")),
         Upsizing = as.numeric(Upsizing),
         NYHA_Heart_Fail_Class  = as.factor(if_else(NYHA_Heart_Fail_Class <3, "0-2", "3-4") ),
         Urgency = as.factor(if_else(Sx_Urgency == 1, "Elective surgery", "Urgent surgery")),
         Sx_Surgeon = ifelse(n > 100, Sx_Surgeon, "other surgeons"),
         Prosthesis_Anat_Aort_Valve = as.factor(case_when(Prosthesis_Anat_Aort_Valve == 0 ~ "3x",
                                                          Prosthesis_Anat_Aort_Valve == 1 ~ "2x",
                                                          Prosthesis_Anat_Aort_Valve == 2 ~ "3x")),
         Event_death = OS_Event,
         DUR = DUR/365.25) %>% 
  mutate(Sx_Surgeon = case_when(Sx_Surgeon == "Ltd. OÄ Dr. med. G. Färber" ~ "GF",
                             Sx_Surgeon == "OA Dr. med. M. Diab" ~ "MD",
                             Sx_Surgeon == "OA Dr. med. T. Sandhaus" ~ "TS",
                             Sx_Surgeon == "PD Dr. med. M. Richter" ~ "MR",
                             Sx_Surgeon == "Prof. Dr. med. T. Doenst" ~ "TD",
                             Sx_Surgeon == "other surgeons" ~ "other")) %>% 
  rename(Surgeon = Sx_Surgeon) -> df4

# Imputation methods
 imp <- mice(df4, meth = "pmm", seed = 123) # Predictive Mean Matching
# imp_midastouch <- mice(df4, meth = "midastouch", seed = 123) # Weighted predictive mean matching
# imp_sample <- mice(df4, meth = "sample", seed = 123) # Random sample from observed values
# imp <- mice(df4, meth = "cart", seed = 123) # Classification and Regression Trees
# imp <- mice(df4, meth = "rf", seed = 123) # Random Forest  
# imp_mean <- mice(df4, meth = "mean", seed = 123) # Mean
# imp <- mice(df4, meth = "norm", seed = 123) # Bayesian linear regression
# imp_norm_nob <- mice(df4, meth = "norm.nob", seed = 123) # Linear regression ignoring model error
# imp_norm_boot <- mice(df4, meth = "norm.boot", seed = 123) # Linear regression using bootstrap
# imp_norm_predict <- mice(df4, meth = "norm.predict", seed = 123) # Linear regression, predicted values
# imp_lasso.norm <- mice(df4, meth = "lasso.norm", seed = 123) # Lasso linear regression
# imp_lasso.select.norm <- mice(df4, meth = "lasso.select.norm", seed = 123) #  Lasso select + linear regression
# imp_quadratic <- mice(df4, meth = "quadratic", seed = 123) #  Imputation of quadratic terms
# imp_ridge <- mice(df4, meth = "ridge", seed = 123) # Random indicator for nonignorable data
```

```{r}
imp_destr <- mice::complete(imp, 'long', include = TRUE) %>%
  mutate(Upsizing = as.factor(if_else(Upsizing == 0, "Anatomical_Size", "UP_size", )))

imp_destr <- as.mids(imp_destr)

complete(imp, 'long', include = FALSE)
```

```{r eval=FALSE}

fit <- with(imp_destr, coxph(Surv(time = DUR, event = OS_Event) ~ Upsizing + Prosthesis_Anat_Size + Age + Surgeon + BMI + Gender + log10(STS+1) + NYHA_Heart_Fail_Class + Prosthesis_Anat_Aort_Valve))

summary(pool(fit))
pool(fit)

tbl_regression(fit, exp = TRUE) %>% 
  add_n(location = "level")

tbl <- tbl_regression(fit, exp = TRUE)

tbl_merge(list(tbl_full %>% add_n(location = "level"), tbl %>% add_n(location = "level")), tab_spanner = c("only Known data", "data with NA"))

  


```

```{r}

```

